---
title: "Animations"
author: "Adam Grünwald"
date: '2019-11-26'
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library('gganimate')
library('gifski')
library('png')
library('transformr')
library('tidyverse')
```

## Presentation by Adam Grünwald

In this presentation I play around with gganimate (https://cran.r-project.org/web/packages/gganimate/gganimate.pdf).

I try some different options to present the iris dataset as well as visualizing some different polynomial regressions fit to synthetic data. In the final slide I have tried a time series animation which I think looks really neat!

## Static plot

```{r static}
p <- ggplot(iris, aes(x = Petal.Width, y = Petal.Length)) + 
    geom_point()

plot(p)

```

## Animated plot

```{r animation}
anim <- p + 
        transition_states(Species,
                          transition_length = 2,
                          state_length = 1) +
        ease_aes('cubic-in-out')

animate(anim)
```

## Not so smooth animation

```{r not smooth}
p <- ggplot(iris, aes(x = Petal.Width, y = Petal.Length)) + 
        geom_point(aes(group = seq_along(Species)))

anim <- p + 
        transition_states(Species,
                          transition_length = 2,
                          state_length = 1) +
        ease_aes('cubic-in-out') +
        ggtitle('Now showing {next_state}',
                subtitle = 'Frame {frame} of {nframes}')

animate(anim)
```

## Another animation

```{r colored animation}
p <- ggplot(iris, aes(x = Petal.Width, y = Petal.Length)) + 
        geom_point(aes(colour = Species, group = 1L))

anim <- p + 
        transition_states(Species,
                          transition_length = 2,
                          state_length = 1) +
        ease_aes('cubic-in-out') +
        ggtitle('Now showing {next_state}',
                subtitle = 'Frame {frame} of {nframes}')

animate(anim)
```

## Animation with fade

```{r fade animation}
p <- ggplot(iris, aes(x = Petal.Width, y = Petal.Length)) + 
        geom_point(aes(colour = Species), size = 2)

anim <- p + 
        transition_states(Species,
                          transition_length = 2,
                          state_length = 1)
animate(anim + 
            enter_fade() +
            exit_shrink())
```

## Line animations

```{r line animation}
set.seed(123)
x = runif(500)
mu = sin(2*(4*x-2)) + 2*exp(-(16^2)*((x-.5)^2))
y = rnorm(500, mu, .3)
d = data.frame(x,y)

mod_poly2 = lm(y ~ poly(x, 2))
poly2 = data.frame(x = x, y = as.numeric(predict(mod_poly2)))[order(x),]

mod_poly3 = lm(y ~ poly(x, 3))
poly3 = data.frame(x, y = as.numeric(predict(mod_poly3)))[order(x),]

mod_poly4 = lm(y ~ poly(x, 4))
poly4 = data.frame(x, y = as.numeric(predict(mod_poly4)))[order(x),]

mod_poly5 = lm(y ~ poly(x, 5))
poly5 = data.frame(x, y = as.numeric(predict(mod_poly5)))[order(x),]

polynomialDf = tibble(x = poly2$x, second = poly2$y, third = poly3$y, fourth = poly4$y, fifth = poly5$y) %>%
    gather(key = 'variable', value = 'value', -x)
polynomialDf$variable = factor(polynomialDf$variable, levels = c('second', 'third', 'fourth', 'fifth'))


p = ggplot() +
        geom_point(data = d, aes(x = x, y = y), color = 'red', alpha = 1/4) +
        geom_line(data = polynomialDf, aes(x = x, y = value, colour = variable, group = variable))

anim = p +
        transition_states(variable,
                          transition_length = 2,
                          state_length = 1)

animate(anim)
```

## Time series animations

```{r time series}
airq <- airquality
airq$Month <- format(ISOdate(2004,1:12,1),"%B")[airq$Month]

anim = ggplot(airq, aes(Day, Temp, group = Month)) + 
        geom_line() + 
        geom_segment(aes(xend = 31, yend = Temp), linetype = 2, colour = 'grey') + 
        geom_point(size = 2) + 
        geom_text(aes(x = 31.1, label = Month), hjust = 0) + 
        transition_reveal(Day) + 
        coord_cartesian(clip = 'off') + 
        labs(title = 'Temperature in New York', y = 'Temperature (°F)') + 
        theme_minimal() + 
        theme(plot.margin = margin(5.5, 40, 5.5, 5.5))

animate(anim)
```