---
title: "MyPresentation"
author: "Adam Grünwald"
date: '2019-11-25'
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

set.seed(123)
x = runif(500)
mu = sin(2*(4*x-2)) + 2*exp(-(16^2)*((x-.5)^2))
y = rnorm(500, mu, .3)
d = data.frame(x,y)

color <- rep(2, length(y))
color_transparent <- adjustcolor(color, alpha.f = 0.3)

mod_poly2 = lm(y ~ poly(x, 2))
poly2 = data.frame(x, as.numeric(predict(mod_poly2)))

mod_poly3 = lm(y ~ poly(x, 3))
poly3 = data.frame(x, as.numeric(predict(mod_poly3)))

mod_poly4 = lm(y ~ poly(x, 4))
poly4 = data.frame(x, as.numeric(predict(mod_poly4)))

mod_poly5 = lm(y ~ poly(x, 5))
poly5 = data.frame(x, as.numeric(predict(mod_poly5)))
```

## My new slide
Some content


## My title

- Bullet one
- Bullet two

1. Item a
2. Item b

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## Slide with my plot

```{r, fig.align='center', fig.cap='My Great Poly', fig.height=4.75}
plot(x, y, pch=20, col = color_transparent)
lines(poly2[order(x),], col = 3)
lines(poly3[order(x),], col = 4)
lines(poly4[order(x),], col = 5)
lines(poly5[order(x),], col = 6)
legend(0.82, 2.2, legend=c("2nd degree", "3rd degree", "4th degree", "5th degree"),
       col=3:6, lty=1, cex=0.8)
```


## Here's some car info

```{r, echo=TRUE, comment=""}
head(mtcars)
```

## It's all git from here

- It's important to master git

That's why I am practicing
